Constructing Sailing Match Race Schedules: round robin pairing lists

### 2015-03-23 paper.tex
added in criteria 5 to list
fixed equation 27

\section{The Constraint Models}
The schedules are produced in 4 stages. The first stage produces a schedule that respects criteria 1, 4, 11 and 12 and minimises criteria 10 (boat changes). The second stage constructs a schedule that respects criteria 1,4,11,12 again and has criteria 10 as a hard constraint generated from first stage and minimises criteria 6 (balance). This results in a schedule that attempts to minimise boat changes \emph{and} balance. The third stage satisfies criteria 9, and is a simple translation of the schedule produced in stage 2.  The final stage, stage 4, orients skippers within matches to address criteria 2, 3 and 8.

@@

\begin{flalign}
& \forall_{i\in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.position_{i,j} \in \{0,1\} \label{posA} \\
& \forall_{i \in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.position_{i,j} = 1 \iff \sigma.timeSlot_{m.j+i} \geq 0 \label{posB} \\
& \forall_{i \in [0..m-1]} ~ imbalance_{i} = |\frac{n-1}{m} - \sum_{j=0}{f-1} position_{i,j}| \label{imbA} \\
& \sigma.maxImbalance = \sigma.maximum(\sigma.imbalance)  \label{imbB}
\end{flalign}

>>>>

\section{The Constraint Models}
The schedules are produced in 4 stages. The first stage produces a schedule that respects criteria 1, 4, 11 and 12 and minimises criteria 10 (boat changes). The second stage constructs a schedule that respects criteria 1,4,11,12 again and has criteria 10 as a hard constraint generated from first stage and minimises criteria 6 (balance). This results in a schedule that attempts to minimise boat changes \emph{and} balance. The third stage satisfies criteria 9, and is a simple translation of the schedule produced in stage 2.  The final stage, stage 4, orients skippers within matches to address criteria 2, 3, 5 and 8.

@@

\begin{flalign}
& \forall_{i\in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.position_{i,j} \in \{0,1\} \label{posA} \\
& \forall_{i \in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.position_{i,j} = 1 \iff \sigma.timeSlot_{m.j+i} \geq 0 \label{posB} \\
& \forall_{i \in [0..m-1]} ~ imbalance_{i} = |\frac{n-1}{m} - \sum_{j=0}^{f-1} position_{i,j}| \label{imbA} \\
& \sigma.maxImbalance = \sigma.maximum(\sigma.imbalance)  \label{imbB}
\end{flalign}
